Anomalous waves triggered by abrupt depth changes: experiments and truncated KdV theory

### 2019-10-12 paper2_JNLS/paper.tex
NM

	Recall that the abrupt depth change is met by traveling waves at time $T_{ADC} = 0$, set to zero for convenience. The KdV equations describe wave dynamics over {\em long} timescales, $t \gg \timescale$, capturing weakly nonlinear and weakly dispersive effects. Meanwhile, evolution over shorter timescales is simply described by linear theory. The event of a wave crossing the ADC is precisely such a short-time event, and so we will employ matching conditions at the ADC that result from linear theory.

@@

	Now, from the perspective of statistical mechanics, consider the communication between the statistical ensembles, $\Gupdn$, upstream and downstream of the ADC. These two systems are in contact at the ADC, and so the upstream state $\Gup$ can be regarded as a thermal reservoir that influences the downstream state $\Gdn$. In fact, the above deterministic  condition directly leads to a simple description for the link. The quantity of interest is the outgoing Hamiltonian $\Hdn$, since its value at $t=0^{-}$ is set by the upstream dynamics, and then this particular value is conserved thereafter in the downstream dynamics. Since $u$ matches at the ADC, so must $\Hdn$, and, in fact, this matching holds for every individual trajectory. Recall that $\Hdn(t)$ is not conserved in the upstream dynamics and so its value varies for $t < 0$. However, appealing to weak Ergodicity of the system, the ensemble mean $\meanup{\Hdn(t)}$ is expected to be independent of time. In particular, the value $\meanup{\Hdn \vert_{t=0^{-}} }$ is the same as the bare ensemble mean $\meanup{\Hdn}$. Afterwards, the particular value $\Hdn \vert_{t=0^{-}}$ is conserved in the downstream dynamics, on a trajectory-by-trajectory basis and for all time. Thus, the downstream measure $\Gdn$ must recover the ensemble mean $\meanup{\Hdn \vert_{t=0^{-}} }$, which gives the statistical matching condition
\begin{align}
\label{statmatch}
\meanup{\Hdn} = \meandn{\Hdn}
\qquad \mbox{\em Statistical matching condition}
\end{align}

\vsp{5}

\vsp{5}
	The statistical matching condition imposes a relationship between the two inverse temperatures $\thup$ and $\thdn$. In particular, we view $\thup$ as given by the random-state of the incoming wave field. Thus, while we will treat $\thup$ as a free parameter that can be varied to study various possible system states, the downstream $\thdn$ is determined directly by matching statistics at the ADC. In this way, \eqref{statmatch} implies the functional dependence
\begin{equation}
\thdn = \transf \left( \thup \right)
\end{equation}
The {\em transfer function} $\transf$ will be a key link needed to relate the theory to experiments.

>>>>

	Recall that the abrupt depth change is met by traveling waves at dimensionless time $T_{ADC} = 0$, set to zero for convenience. The KdV equations describe wave dynamics over {\em long} timescales, physically $t \gg \timescale$, capturing weakly nonlinear and weakly dispersive effects. Meanwhile, evolution over shorter timescales is simply described by linear theory. The event of a wave crossing the ADC is precisely such a short-time event, and so we will employ matching conditions at the ADC that result from linear theory.

@@

	Now, from the perspective of statistical mechanics, consider the communication between the statistical ensembles, $\Gupdn$, upstream and downstream of the ADC. These two systems are in contact at the ADC, and so the upstream state $\Gup$ can be regarded as a thermal reservoir that influences the downstream state $\Gdn$. In fact, the above deterministic  condition directly leads to a simple description for the link. The quantity of interest is the outgoing Hamiltonian $\Hdn$, since its value just upstream of the ADC, $t=0^{-}$, is set by the upstream dynamics, and then this particular value is conserved thereafter in the downstream dynamics. Since $u$ matches at the ADC, so must $\Hdn$, and, in fact, this matching holds for every individual trajectory. Recall that $\Hdn(t)$ is not conserved in the upstream dynamics and so its value varies for $t < 0$. However, appealing to weak Ergodicity, the ensemble mean $\meanup{\Hdn(t)}$ is expected to be independent of time. In particular, the value $\meanup{\Hdn \vert_{t=0^{-}} }$ is the same as the bare ensemble mean $\meanup{\Hdn}$. Afterwards, the particular value $\Hdn \vert_{t=0^{-}}$ is conserved in the downstream dynamics, on a trajectory-by-trajectory basis and for all $t>0$. Thus, the downstream measure $\Gdn$ must recover the same ensemble mean $\meanup{\Hdn \vert_{t=0^{-}} } = \meanup{\Hdn}$, producing the simple condition
\begin{align}
\label{statmatch}
\meanup{\Hdn} = \meandn{\Hdn}
\qquad \mbox{\em Statistical matching condition}
\end{align}

	This statistical matching condition imposes a relationship between the two inverse temperatures $\thup$ and $\thdn$. In particular, we view $\thup$ as given by the random-state of the incoming wave field. Thus, while we will treat $\thup$ as a free parameter that can be varied to study various possible system states, the downstream $\thdn$ is determined directly by the matching condition \eqref{statmatch}, giving the functional dependence
\begin{equation}
\thdn = \transf \left( \thup \right)
\qquad \mbox{\em Transfer function}
\end{equation}
The {\em transfer function} $\transf$ will be a key link needed to relate the theory to experiments.
